A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-19 ms.tex
minor minor fixes
Closing in on submission. small small changes and a recompile

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization \citep{Parsons:2012p9028,Beardsley:2012p9136,Jelic:2008p2130}.
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% flux uncertainty between current telescopes \citep{Jacobs:2013p9908}.

>>>>

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization \citep{Parsons:2012p9028,Beardsley:2013p9952,Jelic:2008p2130}.
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% flux uncertainty between current telescopes \citep{Jacobs:2013p9908}.
